### 2025-07-10 factor-analysis.qmd
20250710 - clean up code

@@

```{r}
#efaVars <- c(
#  "completionsPerGame","passing_yardsPerGame","passing_tdsPerGame",
#  "avg_completed_air_yards","avg_intended_air_yards","avg_air_distance",
#  "passing_cpoe","pass_comp_pct","passer_rating","completion_percentage_above_expectation")

#efaVars <- c(
# "passing_yardsPerGame","passing_tdsPerGame",
# "avg_completed_air_yards","avg_air_distance",
# "pass_comp_pct","passer_rating")
#
#cfaVars <- c(
# "completionsPerGame","attemptsPerGame","passing_yardsPerGame","passing_tdsPerGame",
# "passing_air_yardsPerGame","passing_yards_after_catchPerGame","passing_first_downsPerGame",
# "avg_completed_air_yards","avg_intended_air_yards","aggressiveness","max_completed_air_distance",
# "avg_air_distance","max_air_distance","avg_air_yards_to_sticks","passing_cpoe","pass_comp_pct",
# "passer_rating","completion_percentage_above_expectation"
#)

#faVars <- unique(c(cfaVars, efaVars))

efaVars <- c(
 "completionsPerGame","attemptsPerGame","passing_yardsPerGame","passing_tdsPerGame",
 "passing_air_yardsPerGame","passing_yards_after_catchPerGame","passing_first_downsPerGame",
 "avg_completed_air_yards","avg_intended_air_yards","aggressiveness","max_completed_air_distance",
 "avg_air_distance","max_air_distance","avg_air_yards_to_sticks","passing_cpoe","pass_comp_pct",
 "passer_rating","completion_percentage_above_expectation"
)
```

@@

dataForFA_standardized[faVars] <- scale(dataForFA_standardized[faVars])
#dataForFA[faVars] <- scale(dataForFA[faVars])
```

@@

efa_fit <- lavaan::efa(
  data = dataForFA,
  ov.names = efaVars,
  nfactors = 1:7,
  rotation = "geomin",
  missing = "ML",
  estimator = "MLR",
  bounds = "standard",
  meanstructure = TRUE,
  em.h1.iter.max = 2000000)
```

>>>>

```{r}
#| include: false

@@

```{r}
faVars <- c(
 "completionsPerGame","attemptsPerGame","passing_yardsPerGame","passing_tdsPerGame",
 "passing_air_yardsPerGame","passing_yards_after_catchPerGame","passing_first_downsPerGame",
 "avg_completed_air_yards","avg_intended_air_yards","aggressiveness","max_completed_air_distance",
 "avg_air_distance","max_air_distance","avg_air_yards_to_sticks","passing_cpoe","pass_comp_pct",
 "passer_rating","completion_percentage_above_expectation"
)
```

@@

dataForFA_standardized[faVars] <- scale(dataForFA_standardized[faVars])
```

@@

efa_fit <- lavaan::efa(
  data = dataForFA,
  ov.names = faVars,
  nfactors = 1:7,
  rotation = "geomin",
  missing = "ML",
  estimator = "MLR",
  bounds = "standard",
  meanstructure = TRUE,
  em.h1.iter.max = 2000000)
```
